---
title: "PowerCurve"
author: "Zijie Huang"
date: "2021/2/10"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","knitr")
```

### Build Function
We first build the functions of $\alpha$ and $\beta$.
\begin{align*}
& \alpha(p)=\sum_{m\leq k\leq n}b(n,p,k)\\
& \beta(p)=1-\sum_{m\leq k\leq n}b(n,p,k)
\end{align*}

```{r}
#function of alpha and beta
alpha <- function(m,n,p){
  tmp <- 0
  for (i in m:n) {
    tmp <- tmp + dbinom(i,n,p)
  }
  return(tmp)
}

beta <- function(m,n,p){
  tmp <- 0
  for (i in m:n) {
    tmp <- tmp + dbinom(i,n,p)
  }
  return(1-tmp)
}
```

### Find Critical Value
\begin{align*}
& \alpha(0.6)=\sum_{m\leq k\leq 100}b(100,0.6,k) <0.05\\
\Longrightarrow {} & m>69\\
\end{align*}
\begin{align*}
& \beta(0.8)=1-\sum_{m\leq k\leq 100}b(100,0.8,k) <0.05\\
\Longrightarrow {} & m<73\\
\end{align*}

```{r}
#calculate critical points
n <- 100
p1 <- 0.6
p2 <- 0.8
type1 <- rep(0,100)
type2 <- rep(0,100)

for (i in 1:100) {
  type1[i] <- alpha(i,n,p1)
}
m1 <- min(which(type1<0.05))

for (i in 1:100) {
  type2[i] <- beta(i,n,p2)
}
m2 <- max(which(type2<0.05))

cat("Smallest m to let type-I error < 0.05:",m1,
    "\nLargest m to let type-II error < 0.05:",m2)
```

### Plor Curve
The left curve is using $m=69$ and the right curve is using $m=73$ which are the two critical values we get in the previous section. Since we require the type-I error and the type-II error to be smaller than 0.05, the value of these two curves should lie between $0.05$ and $1-0.05$ for a given range of $p$. Then, what is this range or value? For type-I error, we choose $p=0.6$. For type-II error, we choose $p=0.8$. Therefore, the range should be betweeen $0.6$ and $0.8$.
```{r}
#plot
AlphaCurve1 <- function(x){
  sum(dbinom(69:100,100,x))
}

AlphaCurve2 <- function(x){
  sum(dbinom(73:100,100,x))
}

AlphaCurve1<-Vectorize(AlphaCurve1)
AlphaCurve2<-Vectorize(AlphaCurve2)

ggplot(data.frame(x=c(0.4,1)), aes(x=x)) + 
  stat_function(fun=AlphaCurve1)+
  stat_function(fun=AlphaCurve2)+
  geom_rect(aes(xmin = 0.6, xmax = 0.8, ymin = 0.05, ymax = 0.95),
               fill = "transparent", color = "grey", size = 0.5)+
  scale_x_continuous(breaks = seq(0.4,1,0.1), minor_breaks = NULL)+
  scale_y_continuous(breaks = seq(0,1,0.1), minor_breaks = NULL)+
  theme_classic()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```
